---

title : Rankers
subtitle : A result analysis App
author : Shivee Pradeep Gupta
job :
framework : io2012 # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js # {highlight.js, prettify, highlight}
hitheme : tomorrow #
ext_widgets : {rCharts: ["libraries/highcharts", "libraries/nvd3", "libraries/morris","libraries/mathjax"]} # {mathjax, quiz, bootstrap}
mode : selfcontained # {standalone, draft}
---

## What it does ?
Gives you the following analysis for your entered score:-
<ul><li>Percentile</li>
<li>Student above your score</li>
<li>Students below your score</li>
<li>Number of backlog Students</li></ul>
---
You can choose from following three departments:-
<ul><li>Entc</li>
<li>IT</li>
<li>Comp</li></ul>

---

## Percentile Graph
 
```{r setup, message = F, echo = F, cache = F}
require(rCharts)
knitr::opts_chunk$set(comment = NA, results = 'asis', tidy = F, message = T)
```
 
```{r chart1, echo=FALSE}
score <- read.table("Entc")
pass <- sort(grep("[0-9]",score$V1,value=TRUE))
n= c()
for( i in 1:length(pass)){
n[i] = sum(pass<=pass[i])
}
mydata <- data.frame(pass,n)
mychart<-nPlot(n~pass,data=mydata,type='lineChart')
mychart$params$xAxis = "pass"
mychart$print('chart3')
```
<p><center> Graphical representation of the student's percentile</center></p>
<ul><li>X-axis : Total score acquired</li>
<li> Y-axis : Number of students below that score</li>

---

## The Mathematics involved

<br></br><p>The percentile formula is as follows:</p>
$$latex
percentile = \frac{Number\ of\ students\ below\ the\ score}{Total\ number\ of\ students}
$$

<br><p>The code implementation is as follows:</p>
<p><center> 
percentile[i]= sum(sorted_list_of_scores <= sorted_list_of_scores[i])
<center></p> 

---

## Salient Features

To the geeks (like me ) who give a damn...
<br>This is a :<br>
<ul><li> A self explanatory interactive application with dynamic responses</li>
<li> Modular code </li>
<li> All data is read from files thus making the application extensible</li>
<li> The file names are a list and thus easily refactorable </li>
</ul> 
---

And finally...<br>
<a href = "https://github.com/shiveeg1/Result-Analysis">link to application code on github </a>

<a href = " http://shiveegupta.shinyapps.io/rankers">link to the application on shinyapps.io</a>
<center>Thank You.</center>
















